Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2015-11-08 draft.tex
change format of lemmas to match defns

\newtheorem{definition}{Definition}
\newtheorem{proposition}{Proposition}
\newcommand{\ta}{\theta}
\newcommand{\Ta}{\Theta}
\newcommand{\ga}{\gamma}
\newcommand{\un}{\underline}
\newcommand{\ov}{\overline}
\newcommand{\de}{\delta}
\newcommand{\ve}{\varepsilon}
\linespread{1.05} % Palatino needs more leading (space between lines)
\title{Unrecognized States: A Theory of Self-Determination and Foreign Influence}

@@

These conditions for the status quo are sufficient but not necessary. For example, if the status quo initially has a much higher long term payoff than the next best alternative for the secessionists, Condition (6) need not be met to maintain the status quo in the short run. The inequality \emph{will} bind for some set of periods $t \geq 1$ because the secessionist payoffs from the status quo decrease over time. In cases where condition (6) is not met, we can have unrecognized statehood for some time, but it is not a long-run equilibrium outcome.

\noindent {\bf Proof of Proposition 1} \\
Recall that each period is composed of three action stages: player $p$'s investment decision (stage 1), player $c$'s investment decision (stage 2), and the simultaneous game between players $g$ and $s$ (stage 3). Although period $t$ may be reached either because in period $t-1$ both players ceded or the status quo had been maintained, the strategic landscape in period $t$ is the same. Thus all periods in which the players are able to move are in an equivalence class in which the only possible strategic difference is in the value of the state variables.

@@

\begin{quotation}
\noindent \textit{{\bf Lemma 1:} $Q_{it} \geq L_{it}$ and $\frac {Q_{it}}{1-\delta} \geq  -\zeta_i+\frac{W_{it}(p_{1i}) + L_{it}(1-p_{1i})}{1-\delta}$ for $i \in \left\{g,s\right\}$ are sufficient for status quo to be the outcome of Stage 3 in period $t \ \forall t$.} 
\end{quotation}

@@

\begin{quotation}
\noindent \textit{{\bf Lemma 2:} When Condition 3 holds, the patron's willingness to invest to maintain the status quo is sufficient to deter the international community from intervening to encourage reunification.}
\end{quotation}

@@

\begin{quotation}
\noindent \textit{{\bf Lemma 3:} When Condition 4 holds, the international community's willingness to invest to avoid recognition of the secessionist state is sufficient to deter the patron from investing to achieve recognition.}
\end{quotation}

@@

\begin{quotation}
\noindent \textit{{\bf Lemma 4:} Conditions 3 and 4 ensure that the international community's willingness to invest to discourage new conflict is sufficient to deter the patron from investing to instigate such fighting.}
\end{quotation}

>>>>

\newtheorem{definition}{Definition}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newcommand{\ta}{\theta}
\newcommand{\Ta}{\Theta}
\newcommand{\ga}{\gamma}
\newcommand{\un}{\underline}
\newcommand{\ov}{\overline}
\newcommand{\de}{\delta}
\newcommand{\ve}{\varepsilon}
\linespread{1.05} % Palatino needs more leading (space between lines)
\title{Unrecognized States: A Theory of Self-Determination and Foreign Influence}

@@

The restrictions on the class of games in $\mathcal{G}$ are sufficient but not necessary. For example, if the status quo initially has a much higher long term payoff than the next best alternative for the secessionists, Condition (6) need not be met to maintain the status quo in the short run. The inequality \emph{will} bind for some set of periods $t \geq 1$ because the secessionist payoffs from the status quo decrease over time. In cases where condition (6) is not met, we can have unrecognized statehood for some time, but it is not a long-run equilibrium outcome.

\vskip.1in
\noindent {\bf Proof of Proposition 1} \\
Recall that each period is composed of three action stages: player $p$'s investment decision (stage 1), player $c$'s investment decision (stage 2), and the simultaneous game between players $g$ and $s$ (stage 3). Although period $t$ may be reached either because in period $t-1$ both players ceded or the status quo had been maintained, the strategic landscape in period $t$ is the same. Thus all periods in which the players are able to move are in an equivalence class in which the only possible strategic difference is in the value of the state variables.

@@

\begin{lemma}
$Q_{it} \geq L_{it}$ and $\frac {Q_{it}}{1-\delta} \geq  -\zeta_i+\frac{W_{it}(p_{1i}) + L_{it}(1-p_{1i})}{1-\delta}$ for $i \in \left\{g,s\right\}$ are sufficient for (Status Quo,Status Quo) to be the outcome of Stage 3 in period $t \ \forall t$. 
\end{lemma}

@@

\begin{lemma}
When Condition 3 holds, the patron's willingness to invest to maintain the status quo is sufficient to deter the international community from intervening to encourage reunification.
\end{lemma}

@@

\begin{lemma}
When Condition 4 holds, the international community's willingness to invest to avoid recognition of the secessionist state is sufficient to deter the patron from investing to achieve recognition.
\end{lemma}

@@

\begin{lemma}
Conditions 3 and 4 ensure that the international community's willingness to invest to discourage new conflict is sufficient to deter the patron from investing to instigate such fighting.
\end{lemma}
